---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This package serves nothing but to pass Peer-graded Assignment: Building an R Package.

## Continuous Integration status


## Assignment Info

This assessment will ask reviewers the following questions:

* Does this package contain the correct R file(s) under the R/ directory?
* Does this package contain a man/ directory with corresponding documentation files?
* Does this package contain a vignette which provides a meaningful description of the package and how it should be used?
* Does this package have at least one test included in the tests/ directory?
* Does this package have a NAMESPACE file?
* Does the README.md file for this directory have a Travis badge?
* Is the build of this package passing on Travis?
* Are the build logs for this package on Travis free of any errors, warnings, or notes?

## Functions

In this package You'll find the following functions fars family function.

`courseraPack::fars_read(filename)`

`courseraPack::fars_map_state(state.num,year)`

## Maps

This package is also able to plot this datas on a map as shown below

```{r echo=FALSE, message=FALSE }
library(readr)
library(dplyr)
library(graphics)
library(maps)
library(tidyr)
library(courseraPack)
```

```{r, fig.show='hold'}

 fars_map_state(12,2014)
 
```




